Pretty darn good control: when are approximate solutions better than approximate models

### 2023-06-21 manuscript/manuscript.Rmd
comment on PPO policy evaluation on grid and how the interpolation is done

Policies obtained from the PPO algorithm can be ‘‘noisy’’ as their optimization algorithm is randomized (see, e.g. App. \textbf{TBD} for visualizations of these policies).
We perform some interpolation using a Gaussian process regressor in order to de-noise these policies.
Specifically, we use the *GaussianProcessRegressor* object of the *sklearn* Python library with a kernel given by
\begin{align*}
  \text{RBF}(\text{length scale = 10}) + \text{WhiteNosie}(\text{noise level = 0.1}).
\end{align*}
The length scale and noise level values of this kernel were chosen arbitrarily---no hyperparameter tuning was needed to produce satisfactory interpolation, as will be shown in the results section.

>>>>

Policies obtained from the PPO algorithm can be ‘‘noisy’’ as their optimization algorithm is randomized (see, e.g. App. \textbf{TBD} for visualizations of these policies).
We perform some interpolation using a Gaussian process regressor in order to de-noise these policies.
Specifically, we use the *GaussianProcessRegressor* object of the *sklearn* Python library with a kernel given by
\begin{align*}
  \text{RBF}(\text{length scale = 10}) + \text{WhiteNosie}(\text{noise level = 0.1}).
\end{align*}
This interpolation method is applied to scatter data of the PPO policy evaluated on 3 different grids:
One $51\times 51 \times 5$, one $51\times 5 \times 51$ and one $5\times 51 \times 51$ grid on $(X,Y,Z)$ states.\footnote{
The raw dataset is found at \textbf{TBD} in the repository with the source code and data linked above.
Scatter plots visualizing this policy are shown in App. \textbf{TBD}.
}
The length scale and noise level values of this kernel were chosen arbitrarily---no hyperparameter tuning was needed to produce satisfactory interpolation, as will be shown in the results section.
